---
output: github_document
always_allow_html: true      
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```
#timelineR
### Historical events visualisation in chronological order

Sample data to view events chronologically 
```{r,  echo=TRUE, eval=TRUE, message=FALSE}

tidy_df <- tibble::tibble(year=c(490,847, 1200,1400, 1400, 1700, 1900), event=c( "Marathon","Long throw", "Swimming","Skating","Golf","Surfing","Basketball" ), person=c("Athens", "Greece", "Britan", "Dutch", "Scotland","Polynesia", "USA" ))

knitr::kable(tidy_df)
```

> This is a dummy data, generated only for visualisation purpose

#### Horizontal timeline 
Two features associated with each time-point can be plotted. For instance, the sport first known and the country of origin. 
1. Timeline is plotted horizontally  


```{r,  echo=TRUE,eval=TRUE, message=FALSE, warning=FALSE}
source("R/chronological_timeline.R")
source("R/timeline_theme.R")
chronological_timeline(tidy_df=tidy_df,text = FALSE,horizontal = TRUE)
```

#### Vertical timeline 
2. Timeline is plotted vertically  

```{r,  echo=TRUE,eval=TRUE, message=FALSE, warning=FALSE}
source("R/chronological_timeline.R")
source("R/timeline_theme.R")
chronological_timeline(tidy_df=tidy_df,text = TRUE,horizontal = FALSE)
```

